Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-05-16 prop_letter.tex
prop_letter.tex Small things here and there...

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events~\cite{Kolmogorov1950}. In the quantum case,
the events of interest are specified by \emph{projection operators}
$P$. This set $P$ includes the empty projection~$\mathbb{0}$,
the identity projection~$\mathbb{1}$, projections of the form $\proj{\psi}$
where $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
projections, and products of \emph{commuting} projections. In a well-defined
quantum probability space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is associated with a probability $\mu(P_{i})$
subject to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for a set
of mutually orthogonal projections $\left\{ P_{i}\right\} _{i=1}^{N}$,
we have: 
\begin{equation}
\mu\left(\sum_{i=1}^{N}P_{i}\right)=\sum_{i=1}^{N}\mu\left(P_{i}\right)\textrm{ .}\label{eq:QuantumProbability-Addition}
\end{equation}
\yutsung{Should we define orthogonality between projectors? Also,
in order to compare the Eq.~\ref{eq:QuantumProbability-Addition}
and Eq.~\ref{eq:QuantumInterval-valuedProbability-Inclusion}, maybe
it's better to write just two terms 
\begin{equation}
\mu\left(P_{0}+P_{1}\right)=\mu\left(P_{0}\right)+\mu\left(P_{1}\right)\textrm{ .}\label{eq:QuantumProbability-Addition-1}
\end{equation}
}

@@

We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin-Peres square''
observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{| c | c | c |}
\hline
$\mathbb{1} \otimes\sigma_{z}$ & $\sigma_{z}  \otimes\mathbb{1}$ & $\sigma_{z} \otimes\sigma_{z}$  \\ \hline
$\sigma_{x} \otimes\mathbb{1}$ & $\mathbb{1} \otimes\sigma_{x}$ & $\sigma_{x} \otimes\sigma_{x}$ \\ \hline
$\sigma_{x} \otimes\sigma_{z}$ & $\sigma_{z} \otimes\sigma_{x}$ & $\sigma_{y} \otimes\sigma_{y}$ \\ \hline
\end{tabular}
\label{eq:MerminSquare}
\end{center}

>>>>

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events~\cite{Kolmogorov1950}. In the quantum case,
the events of interest are specified by \emph{projection operators}
$P$. This set includes the empty projection~$\mathbb{0}$, the identity
projection~$\mathbb{1}$, projections of the form $\proj{\psi}$
where $\ket{\psi}$ is a pure quantum state, sums of \emph{orthogonal}
projections, and products of \emph{commuting} projections. In a well-defined
quantum probability space~\cite{10.2307/2308516,gleason1957,Redhead1987-REDINA,Maassen2010},
each event $P_{i}$ is associated with a probability $\mu(P_{i})$
subject to the following axioms: $\mu(\mathbb{0})=0$, $\mu(\mathbb{1})=1$,
$\mu\left(\mathbb{1}-P\right)=1-\mu\left(P\right)$, and for each
pair of \emph{orthogonal} projections $P_{0}$ and $P_{1}$, we have:
\begin{equation}
\bar{\mu}\left(P_{0}P_{1}\right)\subseteq\bar{\mu}\left(P_{0}\right)+\bar{\mu}\left(P_{1}\right)\textrm{ ,}\label{eq:QuantumProbability-Addition}
\end{equation}
where $P_{0}$ and $P_{1}$ are called orthogonal if $P_{0}P_{1}=\mathbb{0}$.

@@

We will proceed by assuming a crypto-deterministic QIVMP $\bar{\mu}$
and derive a contradiction using the following nine ``Mermin-Peres square''
observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{center}
\begin{tabular}{|c|c|c|}
\hline 
$\mathbb{1}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\mathbb{1}$  & $\sigma_{z}\otimes\sigma_{z}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\mathbb{1}$  & $\mathbb{1}\otimes\sigma_{x}$  & $\sigma_{x}\otimes\sigma_{x}$ \tabularnewline
\hline 
$\sigma_{x}\otimes\sigma_{z}$  & $\sigma_{z}\otimes\sigma_{x}$  & $\sigma_{y}\otimes\sigma_{y}$ \tabularnewline
\hline 
\end{tabular}
\par\end{center}
